Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
Discuss inter-rater differences in results

Due to differences in evaluators' interpretations (Fig ZZZZ) of whether or not an article had a molecular focus or not, this scoring criteria was dropped from the analysis and is not reported here.

>>>>

The differences between the co-authors' classifications of the article class as `applied` or `fundamental` had no differences in the five articles that were evaluated by all of the co-authors (Figure \@ref(fig:irArtClass)A).
However, differences in evaluators' interpretations of whether or not an article had a molecular focus or not led to this scoring criteria being dropped from the analysis and is not included in this analysis (Figure \@ref(fig:irArtClass)B).

There was reasonable agreement among the authors when evaluating whether software was cited properly or not and freely and openly available (Figure \@ref(fig:irCriteria)A, \@ref(fig:irCriteria)B).
All authors agreed on the evaluation of the computational methods and data availability of all five articles that were scored by each author (Figure \@ref(fig:irCriteria)C, \@ref(fig:irCriteria)C).

The overall reproducibility scores assigned by authors to the five articles evaluated to check for inter-rater differences showed some differences (Figure \@ref(fig:irReproScore)).
The article that had the greatest difference, 13 to 33%, was DOI "10.1007/s12600-021-00902-2" with a standard deviation of `r ir %>% filter(doi == "10.1007/s12600-021-00902-2") %>% summarise(x = round(sd(reproducibility_score), 1))`.
All other articles had standard deviation scores of less than 4 (Table \@ref(tab:interRaterSD)).
However, all article scores largely agreed and fell below 50% (Figure \@ref(fig:irReproScore)).
